\input{settings}


\begin{document}

\begin{center}
\textbf{\large{Math Logic and Life}}

\textbf{Midterm}
\end{center}

\begin{enumerate}
	\item Find the truth set of the propositional function $(x^2 + 1)(x - 3)(x^2 - 2)(2x - 3) = 0$, when it is given that the set of meanings of this propositional function is each of the following
	
	(a)$Z$(b)$Q$(c)$R$(d)$C$
	
	\item Both of the following statements have the set of positive real numbers as their set of meanings. Which statement is true?
	
	a) $(\exists y)(\forall x)(x < 2y)$ b)$(\forall x)(\exists y)(x < 2y)$
	
	\item Write the converse and contrapositive of the following expression: "If $\sqrt{2} < \sqrt{5}$, then $2 < 5$."
	
	\item Suppose statement $P:(\forall x)(\exists y)(x < 2y)$. Write statement $/sim P$
	
	\item Determine which of the following expressions are tautologies.
	
	(a) $P \rightarrow P$
	
	(b) $P \cap (Q \cup R) \leftrightarrow (P \cap Q) \cup (P \cap R)$
	
	(c) $P \cup Q \leftrightarrow (\sim P \rightarrow Q)$
	\item Assume that "Tim is a boy" is a true statement and that "Tim is ten years old" is a true statement. Which of the following are true?
	
	a) Tim is not a boy and Tim is ten years old
	
	b) If Tim is not a boy then Tim is ten years old
	
	c) Tim is ten years old or Tim is a boy
	
	d) If Tim is not ten years old then Tim is not a boy
	\item Show that $(P \rightarrow Q) \cap (P \cap (\sim Q))$ is a contradiction.
	
	\item Which of the following are propositions?
	
	\item Determine which of the following statements are true
	\begin{enumerate}
		\item If $A \supseteq B$, then $A = B$
		\item Since $\emptyset$ is a set that is a member of every set, there is a set that is a number of every set
		\item If $A = B$, then $A \supset B$
		\item If sets $A = \{1,3,5\}$ and $B = \{1,3,7\}$ then $A \cap B = \{1,3\}$
		\item $\{\{ 1,2,3\}\} \in N \cup P(N)$
		\item $\{\{ 1,2,3\}\} \subseteq N \cup P(N)$
		\item The empty set is a subset of every set.
		\item If sets $A = \{1,2,3,4,5,6\}$ and $B = \{3,4,6\}$ then $A - B = \{1,2\}$
		\item $\{1,2,3\} \in N \cup P(N)$
		\item $\{1,2,3\} \subseteq P(N)$
	\end{enumerate}
	
	\item Write a useful negation of each of the following propositions.
	
	a) If $1 \neq 3$, then $f(1) \neq f(3)$ b) If $a > b$, then $a^2 > b^2$
	
	\item Give are sets $A = \{1,2,3,4,5\}$ and $B = \{2,3,4,5,6,7\}$
	
	\item Finish the following truth table:
	
	\begin{tabular}{|c|c|c|c|c|c|c|}
	\hline
	P & Q & $\sim$P & $\sim$Q & $\sim$P$\vee$Q & P$\wedge\sim$Q & $\sim$Q$\rightarrow \sim$P\\
	\hline
	T&T&&&&&\\
	\hline
	T&F&&&&&\\
	\hline
	F&T&&&&&\\
	\hline
	F&F&&&&&\\
	\hline
	\end{tabular}
	\item Prove that if an integer $n^2$ is even then $n$ is even
	\item If $r$ is real number such that $r^2 = 2$, then $r$ is irrational.
	
	\item Prove or disprove the following statement. For any sets $P,Q$, and $R, (P \cap Q) \cup R = P \cap (Q \cup R)$
	\item Prove that for any natural number $n$, either $n$ is a prime or a perfect square, or $n$ divides $(n - 1)!$.

\end{enumerate}






\end{document}